Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-09-18 article/manuscript.Rnw
comment out related work section

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer questions related specifically to device repair. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{r2}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = \Sexpr{appleHR}, 95\% CI = (\Sexpr{appleLower}, \Sexpr{appleUpper})), factors related to the question's title (e.g., if it was phrased as a question (HR = \Sexpr{titleHR}, 95\% CI = (\Sexpr{titleLower}, \Sexpr{titleUpper}))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = \Sexpr{dayHR}, 95\% CI = (\Sexpr{dayLower}, \Sexpr{dayUpper}))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract} % 174 words

\begin{keywords}
Cox regression; CQA forum; response time; survival analysis; survival probabilty; Kaplan-Meier; 
\end{keywords}

@@

\section{Related Work}

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock2008} also determined that textual features (e.g. word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{Fu2015} instead found non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate a question is of high quality also lead to faster response times.

>>>>

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer device repair-related questions. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{r2}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = \Sexpr{appleHR}, 95\% CI = (\Sexpr{appleLower}, \Sexpr{appleUpper})), factors related to the question's title (e.g., if it was phrased as a question (HR = \Sexpr{titleHR}, 95\% CI = (\Sexpr{titleLower}, \Sexpr{titleUpper}))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = \Sexpr{dayHR}, 95\% CI = (\Sexpr{dayLower}, \Sexpr{dayUpper}))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract} % 174 words

\begin{keywords}
Cox regression; CQA forum; Kaplan-Meier method; response time; survival analysis; survival probabilty;  
\end{keywords}

@@

% \section{Related Work}
% 
% With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework. 
% 
% The majority of existing research has been focused on predicting question and answer quality. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com} using primarily textual features of questions. \cite{Blumenstock2008} also determined that textual features (e.g. word count) was the most accurate predictor of Wikipedia article quality (Wikipedia articles can represent the same kind of user-generated content featured on CQAs). \cite{Fu2015} instead found non-textual features, like revision and comment count or the number of points a user has, were the most useful indicators of quality. A number of other studies have also developed classification algorithms using textual and non-textual features with the similar goal of predicting question or answer quality \cite{Yao2015, Toba2014, Ponzanelli2014a, Ravi2014}. The present analysis seeks to utilize both textual and non-textual features of questions on iFixit's \textit{Answers} forum to investigate if factors that indicate a question is of high quality also lead to faster response times.

### 2018-09-18 article/manuscript.tex
comment out related work section

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer questions related specifically to device repair. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract} % 174 words

\begin{keywords}
Cox regression; CQA forum; response time; survival analysis; survival probabilty; Kaplan-Meier; 
\end{keywords}

>>>>

\begin{abstract} 
iFixit's community-driven online question and answer forum (CQA), \textit{Answers}, provides a platform for thousands of users to ask and answer device repair-related questions. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract} % 174 words

\begin{keywords}
Cox regression; CQA forum; Kaplan-Meier method; response time; survival analysis; survival probabilty;  
\end{keywords}
